\documentclass[margin,line]{res}
\usepackage{hyperref}
\usepackage{url}
\usepackage{setspace}
\usepackage{enumitem}
\oddsidemargin -.5in
\evensidemargin -.5in
\textwidth=6.0in
\itemsep=0in
\parsep=0in
\topmargin=0in
\topskip=0in
 
\newenvironment{list1}{
  \begin{list}{\ding{113}}{%
      \setlength{\itemsep}{0in}
      \setlength{\parsep}{0in} \setlength{\parskip}{0in}
      \setlength{\topsep}{0in} \setlength{\partopsep}{0in}
      \setlength{\leftmargin}{0.17in}}}{\end{list}}
\newenvironment{list2}{
  \begin{list}{$\bullet$}{%
      \setlength{\itemsep}{0in}
      \setlength{\parsep}{0in} \setlength{\parskip}{0in}
      \setlength{\topsep}{0in} \setlength{\partopsep}{0in}
      \setlength{\leftmargin}{0.2in}}}{\end{list}}


    
\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%

\name{\LARGE Smita Raghuvanshi} 

\begin{resume}
\section{\sc Contact Information}

\vspace{.05in}
\begin{tabular}{@{}p{3.5in}p{3in}}
Flat 205,Prime Splendour,Masjid banda,                & {Phone:}  8331827051 \\
Kondapur,Hyderabad,500084                               & {E-mail:}  grtsmitasingh123@gmail.com\\
\\
 %                                                    & {Website:} \url{quicklatex.blogspot.com}  %
\end{tabular}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{\sc Career \\Objective}
Seeking a position where I can implement my technical knowledge and skills acquired through studies, trainings, projects and experience with the best of my potential and contribute to the development of the organization.\\


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


\section{\sc Education}

{\bf Rajiv Academy For Pharmacy} ,UPTU \hfill Year: 2012 - 2014\\
%\vspace*{-.1in}
M.Pharma (Pharmaceutics) \hfill(83.44 \% )

{\bf Amity University} ,U.P \hfill Year: 2008 - 2012\\
%\vspace*{-.1in}
B.Pharma \hfill(8.87 CGPA )

{\bf Sunbeam Academy },Varanasi,UP \hfill Year: 2007 \\
Intermediate \hfill( 74.60 \% )

{\bf Sunbeam Academy},Varanasi,UP \hfill Year: 2005 \\
High School \hfill( 78.40 \%)
\\



%%%%%%%%%%%%%%%%%%%%%%

\section{\sc Professional Experience}

{\bf Shriji Polymers India Ltd, Ujjain}                 \hfill{July,2015 -- Feb,2016}\\
{\em Executive QA, CQA Department} \hfill \\

\begin{itemize} 
\setlength\itemsep{-1em}

\item Worked on SOP/STP and Protocol preparation. Prepared protocol for stability and microbiological studies.\\
\item Worked in internal audit team, checking and verifying state of machines, on going process,documentations and raising tickets for resolutions of the same\\
\item Trained on equipment qualifications ,Vendor management ,Change control and complain handling . My responsibility was to deal directly with Vendors for getting timely VDQ filled by them , informing changes to them and keeping catalog of vendor raw material. This includes filling VDQ from our side.\\

\end{itemize}


%%%%%%%%%%%%%%%%%%%%%%%%%%%



\section{\sc Publications}


Review article on Recent advances in delivery systems and therapeutics of cinnarizine : a poorly water soluble drug with absorption window in stomach, Journal of drug delivery. { \bf Vol. 2014:1-15. Article ID479246, doi.org/10.1155/2014/479246} \vspace{1.5mm}\\
Review article on Oral bioavailability: Issues and solutions via nanoformulations. Clinical pharmacokinetics. { \bf DOI 10.1007/s40262-015-0242-x} \vspace{1.5mm}\\
Research article on Bioadhesive floating microsponges of cinnarizine as novel gastroretentive delivery: Capmul GMO bioadhesive coating versus acconon MC 8-2 EP/NF with intrinsic bioadhesive property, International Journal of Pharmaceutical investigation {\bf  DOI 10.4103/2230-973X.195923} \vspace{1.5mm}





%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{\sc Industrial training}

\begin{itemize} [leftmargin=.1in]
\setlength\itemsep{-1em}
 
\item Six days industrial training at { \bf RANBAXY}, Dewas, M.P.\\
\item One and half month industrial training in Production division at SUPER FORMULATIONS PVT. LTD., Ujjain, M.P . \\
\item One and half month industrial training at SaMa Biotech, Group of ESMA Formulations (P) Ltd., Panchkula, Haryana .\\
\item Three days industrial instrumental training programme at, ONIOSOME HEALTHCARE Pvt. Ltd., Mohali, Punjab . \\
\item Industrial tour at YAKULT PVT. LTD. Sonipat, Harayana .\\

\end{itemize}


%%%%%%%%%%%%%%%%%%%%%%%%%

\section{\sc Awards and Achievements}
\setlength{\parskip}{10pt plus 1pt minus 1pt}

{\bf Gold medalist}, B. Pharm (2012), AMITY University.\vspace{1mm}\\
{\bf 1st} position in poster presentation (UG) at SPIRIT 11, a national level scientific competition organized by Pharmaceutical Society of Department of Pharmaceutics, {\bf IT- BHU}, Varanasi.\vspace{1mm}\\
{\bf 2nd} position in poster presentation (PG) at SPIRIT 14, a national seminar on Challenges, opportunities and futuristic trends in pharmacy education organized by Department of Pharmaceutics, {\bf IT- BHU}, Varanasi.\vspace{1mm}\\
2nd position in poster presentation at CRATDDS-2014: AICTE sponsored national seminar.\vspace{1mm}\\
Continuous On-Academic Merit Scholarship (2008-2012) at Amity University.\vspace{1mm}\\
Life member of Indian Pharmacy Graduates Association.\\


%%%%%%%%%%%%%%%%%%%%%%%


\section{\sc Academic \\Project and dissertation}

The M.Pharm research project entitled { \bf Biadhesive floating microsponges of cinnarizine : Development and evaluation} carried under the supervision of Dr. Mrs. Kamla Pathak, Professor and Head, Department of pharmaceutics, Rajiv Academy for Pharmacy, Mathura\\

%%%%%%%%%%%%%%%%%%%%%%%%%%%%


\section{\sc Seminars and Conferences}

\begin{itemize}[leftmargin=.1in]
\setlength\itemsep{-1em}

\item Attended National Seminar on challenges, opportunities and futuristic trends in pharmacy education, organised by Department of Pharmaceutics, IIT- BHU \\
\item Attended AICTE sponsored National Seminar on current and recent advances in targeted drug delivery system at Kota College of Pharmacy \\

\end{itemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


\end{resume}
\end{document}




